%# -*- coding: utf-8-unix -*-
%%==================================================
%% abstract.tex for SJTU Master Thesis
%%==================================================

\begin{abstract}
随着计算机的发展,我们期望能用一种高效而且准确的方法识别人类的情绪,从而在人机交互与人人交互中发挥巨大的作用。在基于各种信号的情绪识别中,基于脑电信号的情绪识别算法由于与激发情绪的大脑活动有直接关联,无疑成为当前最有可能获得较高准确度的情绪识别算法之一。因此,建立一套能广泛适用于不同个体之间的算法模型有着非常重要的实际意义,也成为当下基于脑电信号的情绪识别研究的热点之一。与此同时，随着机器的计算能力的提高，深度学习的方法例如卷积神经网络，深度置信网络，深度自编码器等受到研究人员的青睐。但是如果只是用单一模态的输入进行学习，由于数据的分布总是相似的，所以提供的信息和学习能力都是很有限的。相反，不同模态譬如声音，文字，图像，脑电，眼动轨迹带有不同信息，所以提供的数据分布各不相同，他们各自提供的信息不但有交集，还互相补充。因此，如果能够利用多模态输入信号的融合，我们不仅可以提取出多模态共有的特征表达，从而找出它们代表的现实世界中的意义，还可以利用多个模态不同信号的互补信息来提高情绪识别任务的准确率。

\keywords{\large 深度学习 \quad 深度自编码器 \quad 多模态 \quad 互补特征}
\end{abstract}

\begin{englishabstract}

An imperial edict issued in 1896 by Emperor Guangxu, established Nanyang Public School in Shanghai. The normal school, school of foreign studies, middle school and a high school were established. Sheng Xuanhuai, the person responsible for proposing the idea to the emperor, became the first president and is regarded as the founder of the university.

During the 1930s, the university gained a reputation of nurturing top engineers. After the foundation of People's Republic, some faculties were transferred to other universities. A significant amount of its faculty were sent in 1956, by the national government, to Xi'an to help build up Xi'an Jiao Tong University in western China. Afterwards, the school was officially renamed Shanghai Jiao Tong University.

Since the reform and opening up policy in China, SJTU has taken the lead in management reform of institutions for higher education, regaining its vigor and vitality with an unprecedented momentum of growth. SJTU includes five beautiful campuses, Xuhui, Minhang, Luwan Qibao, and Fahua, taking up an area of about 3,225,833 m2. A number of disciplines have been advancing towards the top echelon internationally, and a batch of burgeoning branches of learning have taken an important position domestically.

Today SJTU has 31 schools (departments), 63 undergraduate programs, 250 masters-degree programs, 203 Ph.D. programs, 28 post-doctorate programs, and 11 state key laboratories and national engineering research centers.

SJTU boasts a large number of famous scientists and professors, including 35 academics of the Academy of Sciences and Academy of Engineering, 95 accredited professors and chair professors of the "Cheung Kong Scholars Program" and more than 2,000 professors and associate professors.

Its total enrollment of students amounts to 35,929, of which 1,564 are international students. There are 16,802 undergraduates, and 17,563 masters and Ph.D. candidates. After more than a century of operation, Jiao Tong University has inherited the old tradition of "high starting points, solid foundation, strict requirements and extensive practice." Students from SJTU have won top prizes in various competitions, including ACM International Collegiate Programming Contest, International Mathematical Contest in Modeling and Electronics Design Contests. Famous alumni include Jiang Zemin, Lu Dingyi, Ding Guangen, Wang Daohan, Qian Xuesen, Wu Wenjun, Zou Taofen, Mao Yisheng, Cai Er, Huang Yanpei, Shao Lizi, Wang An and many more. More than 200 of the academics of the Chinese Academy of Sciences and Chinese Academy of Engineering are alumni of Jiao Tong University.

\englishkeywords{\large SJTU, master thesis, XeTeX/LaTeX template}
\end{englishabstract}

